### 2025-12-01 multiple-regression.qmd
20251201 - typo

Consider an example where you develop an algorithm to predict players' fantasy performance based on 2024 data using hundreds of [predictor variables](#sec-correlationalStudy).
To some extent, these [predictor variables](#sec-correlationalStudy) will likely account for true variance (i.e., signal) and error variance (i.e., noise).
If we were to apply the same algorithm based on the `r as.integer(format(Sys.Date(), "%Y")) - 1` prediction model to `r as.integer(format(Sys.Date(), "%Y"))` data, the prediction model would likely predict less accurately than with `r as.integer(format(Sys.Date(), "%Y")) - 1` data.
The regression coefficients (and resulting accuracy) tend to become weaker when applied to new data, a phenomenon called [shrinkage](#sec-shrinkage), which is described in @sec-shrinkage.
For instance, shrinking is observed when applying multiple regression models to new data in @sec-fittingModels-regression and when applying [machine learning](#sec-machineLearning) models to new data in @sec-fittingModels-machineLearning.

>>>>

Consider an example where you develop an algorithm to predict players' fantasy performance based on 2024 data using hundreds of [predictor variables](#sec-correlationalStudy).
To some extent, these [predictor variables](#sec-correlationalStudy) will likely account for true variance (i.e., signal) and error variance (i.e., noise).
If we were to apply the same algorithm based on the `r as.integer(format(Sys.Date(), "%Y")) - 1` prediction model to `r as.integer(format(Sys.Date(), "%Y"))` data, the prediction model would likely predict less accurately than with `r as.integer(format(Sys.Date(), "%Y")) - 1` data.
The regression coefficients (and resulting accuracy) tend to become weaker when applied to new data, a phenomenon called [shrinkage](#sec-shrinkage), which is described in @sec-shrinkage.
For instance, shrinkage is observed when applying multiple regression models to new data in @sec-fittingModels-regression and when applying [machine learning](#sec-machineLearning) models to new data in @sec-fittingModels-machineLearning.
